\thispagestyle{empty}

\chapter*{Abstract}
This Master's Thesis presents the design and development of the Learning Ecosystem, a web application created to improve the management of corporate training at Tracasa Global and Tracasa Instrumental. The project responds to the need for a unified digital environment that allows for the efficient coordination of all processes related to employee training, from the initial request to the final assessment of each training action. The tool integrates essential functions such as requesting new training, approval by managers and directors, and monitoring the progress of each process in a single space. It also provides direct access to external learning and cybersecurity platforms, expanding the professional development opportunities available to employees. In addition, it incorporates mechanisms that improve traceability, such as change history, attendee and teacher management, and the collection of evaluations and effectiveness surveys. Another key aspect of the project is the management of annual training plans. The application allows different departments to propose, review, and combine training activities, as well as maintain centralized control of accepted proposals and their relationship to the training courses created. This functionality contributes to more strategic planning that is consistent with the overall needs of the organization. Overall, this work represents a significant step forward in the digitization of corporate training and reinforces the company's commitment to continuous improvement, lifelong learning, and more agile and transparent talent management.


\vspace{1cm}
Keywords: Learning Ecosystem, web application, corporate training, training management, Tracasa Global, Tracasa Instrumental, digitization, training plans.



\clearpage
\thispagestyle{empty}
\hfill
\clearpage